### 2022-04-12 sections/bdt_Htautau.tex
change legend to ell
update BR label and CONF pub data
updatesn new plots and add CR plots

A comparison between data and the predicted background for the leading $\had$ $\pt$ distribution in the SRs, after applying fake factors, 
%some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
is shown in Figure~\ref{fig:taupt_prefit}.
%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_{\ell}hadhad}.
%The comparison between the data and predicted background after preselection for the distributions of two of the most 
%discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
%The expected signals are also shown after scaled up for the shape comparison of the distributions.
%by a large factor normalized to the total number of events in the predicted
%background for the shape comparison.   
%corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
The last bin of each plot contains the overflow entries.
The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.
The hashed area represents the total uncertainty of the background.
A good description of the data by the background model is observed in all cases.
The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_os_log_.pdf} &
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b1j_ss_log_.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf}\\
(d) & (e) \\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}\\
(f) & (g) \\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_h\thadhad$-2j (f), and $t_h\thadhad$-3j (g).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:taupt_prefit}
\end{figure}

@@

>>>>

A comparison between data and the predicted background for the leading $\had$ $\pt$  and visible di-tau mass distribution in the SRs, after applying fake factors, 
%some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
is shown in Figure~\ref{fig:taupt_prefit} and Figure~\ref{fig:mtt}, respectively.
%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_{\ell}hadhad}.
%The comparison between the data and predicted background after preselection for the distributions of two of the most 
%discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
%The expected signals are also shown after scaled up for the shape comparison of the distributions.
%by a large factor normalized to the total number of events in the predicted
%background for the shape comparison.   
%corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
The last bin of each plot contains the overflow entries.
The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.
The hashed area represents the total uncertainty of the background.
A good description of the data by the background model is observed in all cases.
The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_os_log_.pdf} &
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b1j_ss_log_.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf} &
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jss_log_.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
 $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$ same sign CR (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j same sign CR (i).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:taupt_prefit}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_os_log_mtt.pdf} &
\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l1tau1b1j_ss_log_mtt.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_ss_log_mtt.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l1tau1b3j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_ss_log_mtt.pdf}\\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg2mtau1b2jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg2mtau1b3jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg2mtau1b3jss_log_mtt.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Visible di-tau mass  distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
 $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$ same sign CR (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j same sign CR (i).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:mtt}
\end{figure}

\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b2j_os_log_ttCR.pdf} &
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b2j_ss_log_ttCR.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b3j_os_log_ttCR.pdf}\\
(a) & (b) & (c) \\
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b3j_ss_log_ttCR.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg2l1tau1bnj_log_ttCR.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg2l1tau2bnj_log_ttCR.pdf}\\
(d) & (e) & (f)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained the fake $\thad$ calibration method after applying fake factors in the following CRs: 
$t_{\ell}t_{h}$2b$\thad$-2j OS (a), $t_{\ell}t_{h}$2b$\thad$-2j SS (b), $t_{\ell}t_{h}$2b$\thad$-3j OS (c), $t_{\ell}t_{h}$2b$\thad$-3j SS (d), $t_{\ell}t_{\ell}$1b$\thad$-nj (e) and $t_{\ell}t_{\ell}$2b$\thad$-nj (f).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. 
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:ttCR_mtt}
\end{figure}
